### 2023-11-10 Scripts/Manuscript/manuscript.Rmd
added figure 456, and the test result for H4 plus the function used for that to help convert betareg output to apa output.

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(grid)
library(gridExtra)

@@

@@

The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only 52 out of 77 measures in replications, and only ten measures used in original studies were modified. The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.

Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols. Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects ($B = -0.779, SD = 0.140, p < .001$). This result is in line with hypothesis 4.

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)

@@

## Questionable Measurement Practices
The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.

```{r Plot 456 Code}
# plot for alpha
### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
       aes(x = QMP_ratio, fill = RepOrg)) + 
  geom_bar(position = "dodge", stat = "bin", bins = 10) +
  facet_grid(~QMP_type) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_manual(values=c("brown", "blue4")) +
  theme(legend.position = "none") +
  ylab("Count") +
  xlab("QMP Ratio") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
Mean_Rat_Org <- mean(plot_456_data$QMP_ratio[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])

Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

Plot_456_2

# combine both plots into one figure
grid.arrange(Plot_456_1, 
             Plot_456_2, 
             nrow = 2)

Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols. Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (`r betareg_output_to_apa_full(H4_test_results_REV)`). This result is in line with hypothesis 4.

@@
